---
title: "Projection_Simulation"
author: "Janet"
date: "19/05/2021"
output: html_document
---

packages and settings  
```{r}
library(rstanarm)
options(mc.cores = parallel::detectCores())
library(loo)
library(tidyverse)
library(GGally)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(projpred)
SEED=1210
```

Other than the model showed in the "collinear" file, here are the three scenarios I tested:  
### 1.  
targets (y) follow a poisson distribution, but we include the interaction in the construction.  
```{r}
set.seed(SEED)
df <- tibble(
  pos.tot = runif(200,min=0.8,max=1.0),
  urban.tot = pmin(runif(200,min=0.0,max=0.02),1.0 - pos.tot),
  neg.tot = (1.0 - pmin(pos.tot + urban.tot,1)),
  x1= pmax(pos.tot - rnorm(200,min=0.05,max=0.30),0),
  x3= pmax(neg.tot - runif(200,min=0.0,max=0.10),0),
  x2= pmax(pos.tot - x1 - x3/2,0),
  x4= pmax(1 - x1 - x2 - x3 - urban.tot,0))
# true model and 200 Poisson observations

mean.y <- exp(-5.8 + 6.3*df$x1 + 15.2*df$x2 + 7.1*df$x1*df$x2)
df$y <- rpois(200,mean.y)
```

```{r}
fitg <- stan_glm(y ~ x1*x2 + x3 + x4, data = df, na.action = na.fail, family=poisson(), seed=SEED)
summary(fitg)

mcmc_areas(as.matrix(fitg),prob_outer = .99)
```

Now proceed with the projection:  
```{r}
fitg_cv <- cv_varsel(fitg, method='forward', cv_method='LOO')
nv <- suggest_size(fitg_cv, alpha=0.1)
# the suggest_size is 2, only x1 and x2 are included
```

Here is the summary of the posteriors:  
```{r}
projg <- project(fitg_cv, nv = nv, ns = 4000)
round(colMeans(as.matrix(projg)),1)
round(posterior_interval(as.matrix(projg)),1)
```

### 2.  
No interaction involved, but the targets (y) follow a binomial distribution, i.e. logit link:  
```{r}
mean.y2 <- exp(-5.8 + 6.3*df$x1 + 15.2*df$x2)/(1+exp(-5.8 + 6.3*df$x1 + 15.2*df$x2))
df$y2 <- rbinom(200,1,mean.y2)
```

```{r}
fitg2 <- stan_glm(y2 ~ x1 + x2 + x3 + x4, data = df, na.action = na.fail, family=binomial(link = logit), seed=SEED)
summary(fitg2)
```

Proceed with the projection and summarize the result:  
```{r}
fitg_cv2 <- cv_varsel(fitg2, method='forward', cv_method='LOO')
nv2 <- suggest_size(fitg_cv2, alpha=0.1)
# the suggest_size is 1, only x1 included
# could it relate to 'seed=SEED' in the stan_glm ? 

projg2 <- project(fitg_cv2, nv = nv2, ns = 4000)
round(colMeans(as.matrix(projg2)),1)
round(posterior_interval(as.matrix(projg2)),1)
```

### 3.  
Now we keep the $y \sim Poisson$, while change the variables (x1 and x3) to be generated from a normal distribution  
```{r}
dfs <- tibble(
  x1= rnorm(200,mean=0.2,sd=0.05),
  x3= rnorm(200,mean=0.05,sd=0.025),
  x2= - x1 - x3/2,
  x4= 1 - x1 - x2 - x3)

mean.y3 <- exp(-5.8 + 6.3*dfs$x1 + 15.2*dfs$x2)
dfs$y <- rpois(200,mean.y3)
```

```{r}
fitg3 <- stan_glm(y ~ x1 + x2 + x3 + x4, data = dfs, na.action = na.fail, family=poisson(), seed=SEED)
summary(fitg3)
```

Looks good here:  
```{r}
fitg_cv3 <- cv_varsel(fitg3, method='forward', cv_method='LOO')
nv3 <- suggest_size(fitg_cv3, alpha=0.1)
```

```{r}
projg3 <- project(fitg_cv3, nv = nv3, ns = 4000)
round(colMeans(as.matrix(projg3)),1)
round(posterior_interval(as.matrix(projg3)),1)
```
